When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed cursive formatting

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, *n*-back"
wordcount         : "~ 4,300"
bibliography      : CAD.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
always_allow_html : true
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

@@

One task that is often used to investigate effort is the *n*-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six[@Mackworth1959].
The *n*-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times[@Jaeggi2010], and brain activity in areas associated with working memory[@Jonides1997; @Owen2005].
However, its reliability measures are mixed, and associations of *n*-back performance and measures such as executive functioning and fluid intelligence are often inconsistent[@Jaeggi2010].

A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
First, the participants complete the *n*-back levels to familiarize themselves with the task.
Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred[@Westbrook2013].
The subjective value (SV) of each more difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
Westbrook et al.[-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting.
Younger participants showed lower effort discounting, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.

@@

With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
In the present study, we validated the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
Additionally, we compared the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
The full results of the latter are published in a second Registered Report[@ScheffelZerna2022].
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate[@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
As a manipulation check, we hypothesized that with increasing *n*-back level the (1a) the signal detection parameter *d'* declines, while (1b) reaction time and (1c) perceived task load increase.
Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
And finally, we hypothesized that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.

@@

INSERT FIGURE 1 HERE
<!--
```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an *n*-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}

@@

### Study procedure
Healthy participants aged 18 to 30\ years were recruited using the software *ORSEE*[@Greiner2015].
Participants completed the personality questionnaires online and then visited the lab for two sessions one week apart.
NFC was assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
Several other personality questionnaires were used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CAD).
In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
The paradigm started with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this *n*-back level.
After the *n*-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
They were told that one of their choices would be randomly picked for the final run of *n*-back, the data of which was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
After the CAD paradigm, participants filled out a short questionnaire on the tablet, indicating whether they adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).  
The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm followed the same structure of task and effort discounting procedure, but participants could decide which strategy they wanted to reapply in the last block.
Study data was collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)).
The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and *n*-back level influencing SVs.
Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aimed to collect about $50\%$ more data sets than necessary, $N=120$ in total.

@@

Data collection and analysis were not performed blind to the conditions of the experiments.
We excluded the data of a participant from all analyses, if the participant stated that they did not follow the instructions, if the investigator noted that the participant misunderstood the instructions, or if the participant withdrew their consent.
No data was replaced.
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
Aggregated RT values were described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
To test our hypotheses, we performed a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].

*Manipulation check.*
Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
Another rmANOVA with six paired contrasts was computed to compare the median RT between two levels of 1- to 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.

*Subjective values.*
For each effort discounting round, the SV of the fixed level was calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
This yielded an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level was 1.
The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
All SVs of each level were averaged to compute one "global" SV for each level.
An rmANOVA with four different contrasts were computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.

To determine the influence of task performance on the association of SVs and *n*-back level, we performed MLM. 
We applied restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we estimated a random slopes model of *n*-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher *n*-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We controlled for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
$$
SV \sim level\ + d' + median RT + (level|subject)
$$
Level-1-predictors were centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
If necessary, we will adjusted the optimization algorithm to improve model fit. 
We visually inspected the residuals of the model for evidence to perform model criticism. 
This was done by excluding all data points with absolute standardized residuals above 3 SD. 
As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of *n*-back level according to Lorah[-@Lorah2018].
To ensure the validity of the association of SVs and *n*-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The rmANOVA was run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.
The specification curve analysis was linked to the MLM in the initial submission, and was assigned to hypothesis 3a during the review process and in the Stage 1 report.
Afterwards, we noticed that 3a does not contain any RT data, so the specification curve analysis was reassigned to the MLM with the agreement of the editor.

The association of SVs and NFC was examined with an rmANOVA.
We subtracted the SV of 1- from 2-back and 2- from 3-back, yielding two SV difference scores per participant.
The sample was divided into participants with low and high NFC using a median split.
We then computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
Post-hoc tests were computed depending on which effect reached significance at $p<.01$.

The association of subjective task load with NFC was examined similarly.
We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e. as the SV rises, the aversiveness declines, and vice versa.
We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
Then, we computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.

The results of each analysis was assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *ttestBF*.
We considered a $BF10$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF10$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].

@@

The sample of the pilot study consisted of $N=15$ participants (53.3% female, $M=24.43$ ($SD=3.59$) years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=14$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
All results are detailed in the Supplementary Material.

@@

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
Of the $N=`r n_quest`$ participants who filled out the online questionnaires, $n=`r length(datalist_nback)`$ came to the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included $N=`r nrow(data_quest)`$ participants.

@@

The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`).
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
The median RT did not differ between 2-back and 4-back, and the median RT was higher for 3-back than for 4-back (Table\ \@ref(tab:H1b-contrasts)).

```{r H1b-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels",
  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

>>>>

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, $n$-back"
wordcount         : "~ 4,300"
bibliography      : CAD.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
always_allow_html : true
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

@@

One task that is often used to investigate effort is the $n$-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
Participants indicate via button press whether the current stimulus is the same as $n$ stimuli before, with $n$ being the level of difficulty between one and six[@Mackworth1959].
The $n$-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times[@Jaeggi2010], and brain activity in areas associated with working memory[@Jonides1997; @Owen2005].
However, its reliability measures are mixed, and associations of $n$-back performance and measures such as executive functioning and fluid intelligence are often inconsistent[@Jaeggi2010].

A way to quantify the subjective cost of each $n$-back level has been developed by Westbrook, Kester, and Braver[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
First, the participants complete the $n$-back levels to familiarize themselves with the task.
Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred[@Westbrook2013].
The subjective value (SV) of each more difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
Westbrook et al.[-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting.
Younger participants showed lower effort discounting, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.

@@

With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest $n$-back level has the highest SV.
We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different $n$-back levels without presuming that all individuals inherently prefer the easiest level.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
In the present study, we validated the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
Additionally, we compared the effort discounting behavior of participants regarding the $n$-back task and an emotion regulation task.
The full results of the latter are published in a second Registered Report[@ScheffelZerna2022].
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate[@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
As a manipulation check, we hypothesized that with increasing $n$-back level the (1a) the signal detection parameter $d'$ declines, while (1b) reaction time and (1c) perceived task load increase.
Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing $n$-back level, and (2b) they do so even after controlling for declining task performance.
And finally, we hypothesized that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.

@@

INSERT FIGURE 1 HERE
<!--
```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}

@@

### Study procedure
Healthy participants aged 18 to 30\ years were recruited using the software *ORSEE*[@Greiner2015].
Participants completed the personality questionnaires online and then visited the lab for two sessions one week apart.
NFC was assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
Several other personality questionnaires were used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CAD).
In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
The paradigm started with the $n$-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this $n$-back level.
After the $n$-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
They were told that one of their choices would be randomly picked for the final run of $n$-back, the data of which was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
After the CAD paradigm, participants filled out a short questionnaire on the tablet, indicating whether they adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).  
The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm followed the same structure of task and effort discounting procedure, but participants could decide which strategy they wanted to reapply in the last block.
Study data was collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)).
The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and $n$-back level influencing SVs.
Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aimed to collect about $50\%$ more data sets than necessary, $N=120$ in total.

@@

Data collection and analysis were not performed blind to the conditions of the experiments.
We excluded the data of a participant from all analyses, if the participant stated that they did not follow the instructions, if the investigator noted that the participant misunderstood the instructions, or if the participant withdrew their consent.
No data was replaced.
The performance measure $d'$ was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
Aggregated RT values were described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
To test our hypotheses, we performed a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].

*Manipulation check.*
Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing $d'$ between two levels of 1- to 4-back at a time.
Another rmANOVA with six paired contrasts was computed to compare the median RT between two levels of 1- to 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.

*Subjective values.*
For each effort discounting round, the SV of the fixed level was calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
This yielded an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level was 1.
The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
All SVs of each level were averaged to compute one "global" SV for each level.
An rmANOVA with four different contrasts were computed to investigate the association of SVs and the $n$-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.

To determine the influence of task performance on the association of SVs and $n$-back level, we performed MLM. 
We applied restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher $n$-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We controlled for performance, i.e., $d'$ (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
$$
SV \sim level\ + d' + median RT + (level|subject)
$$
Level-1-predictors were centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
If necessary, we will adjusted the optimization algorithm to improve model fit. 
We visually inspected the residuals of the model for evidence to perform model criticism. 
This was done by excluding all data points with absolute standardized residuals above 3 SD. 
As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].
To ensure the validity of the association of SVs and $n$-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within $n$-back levels).
The rmANOVA was run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.
The specification curve analysis was linked to the MLM in the initial submission, and was assigned to hypothesis 3a during the review process and in the Stage 1 report.
Afterwards, we noticed that 3a does not contain any RT data, so the specification curve analysis was reassigned to the MLM with the agreement of the editor.

The association of SVs and NFC was examined with an rmANOVA.
We subtracted the SV of 1- from 2-back and 2- from 3-back, yielding two SV difference scores per participant.
The sample was divided into participants with low and high NFC using a median split.
We then computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
Post-hoc tests were computed depending on which effect reached significance at $p<.01$.

The association of subjective task load with NFC was examined similarly.
We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e. as the SV rises, the aversiveness declines, and vice versa.
We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
Then, we computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.

The results of each analysis was assessed on the basis of both $p$-value and the Bayes factor $BF_{10}$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *ttestBF*.
We considered a $BF_{10}$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF_{10}$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].

@@

The sample of the pilot study consisted of $N=15$ participants (53.3% female, $M=24.43$ ($SD=3.59$) years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=14$ data sets.
The results showed increases in subjective and objective task load measures with higher $n$-back level.
Importantly, SVs were lower for higher $n$-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed $n$-back level as a reliable predictor of SV, even after controlling for declining task performance ($d'$ and median RT).
NASA-TLX scores were higher with higher $n$, and lower for the group with lower NFC scores, but NFC and $n$-back level did not interact.
All results are detailed in the Supplementary Material.

@@

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
All of the $N=`r n_quest`$ participants who filled out the online questionnaires came to the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included $N=`r nrow(data_quest)`$ participants.

@@

The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`).
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
It did not differ between 2- and 4-back, and it was higher for 3- than for 4-back (Table\ \@ref(tab:H1b-contrasts)).

```{r H1b-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```
